\documentclass[11pt]{scrartcl}
\date{}
\usepackage{fullpage}

\title{Understanding Information Leakage in Searchable Encryption \\
-- answer to reviews --}
\begin{document}
\maketitle


We thank the reviewers for their feedback. It was particularly pleasant to see that all reviewers agree that the proposed research addresses a timely and challenging problem through an innovative approach.
They also agree that the project costs are modest, especially since the results we are perceived as as ``transformative''. 

\vspace{.2cm}
Reviewers 094921136 and 033148032 raise two questions regarding i) the necessity and schedule of the envisioned meetings and ii) the focus of the impact on the academic community.

\heading{The need for face to face meetings; their schedule}

Three factors determine the answer to the first question.  The project is relatively short, involves a group of reserchers at three different locations and is theoretical in nature.

The project is theoretical and much of the

exchanging ideas between fields require extensive discussions.
Since the project is relatively short, carrying out sporadic skype meetings, even weekly ones
Avoid thrashing and the multitasking required 

Tentative schedule of the meetings and specific topics:
\begin{itemize}\itemsep-3pt
  \item (August'18) Identify initial schemes, test the feasability of the approach, study computational leakage vs information-theoretic leakage 
\item (Jan-Feb'18) Study composition of schemes. 
\item (June'19) Identify directions of future work 
\end{itemize}

NB: the length of the visits will need to be determined based on availability and teaching commitments still to be determined. While overall we expect that the PI will visit for about 30 days, the precise split between meetings will be determined on the fly. In particular, the first two visits are likely to be longer (e.g. about two weeks each).

\heading{Focus on academic community}
The project is foundational in nature: it aims to understand
In particular, the schemes that we will start with are
Whiel within one year it is reasonble to expect to publish a couple of papers at top conferences and/or focused workshops extending impact beyond 



This makes it crucial that some of the research is carried out 

This project addresses the foundations of searchable encryption and all of the work envisioned is theoretical in nature.   

The project spans a bit more than a year and a half. 






On the one hand this research 


It is a bit difficult to forsee the exact calendar of the proposed visits since they will depend on stil unknown factors (e.g. allocation of teaching duties). 








\end{document}
